\section{Future Scope}
Bluetooth Low Energy is a relatively new technology. This implies that there is a long road ahead of more features, more research and more hardware for this technology. As such there is always room for inclusion in the Linux kernel for all of this. If the completely new hardware is introduced then it becomes very important to have its driver included in Linux. This is not just have the support for the device in Linux but it also acts like an endorsement for the device that its driver has been registered with the coveted Linux kernel.\\
Talking specifically about some of the other Bluetooth Low Energy solutions by ST, following two come to immediate consideration that can also be driven by a Linux host by means of device driver written in a manner much similar to BlueNRG:
\begin{enumerate}
	\item \textbf{BlueNRG-MS}
	\item \textbf{BlueNRG 1}
\end{enumerate}
The continuous need for more software related to BLE in Linux is not just restricted to device driver development. Bluez is the official Bluetooth stack for Linux but even it does not implement everything in the Bluetooth 4.1 specification. Some features are missing and are intended for the future. Also since with new specification releases, more and more features get introduced into the technology. So the stack will also have to sustain with the specification. Some of the things that are not yet implemented in Bluez but are part of the Bluetooth specification are:
\begin{itemize}
	\item Random address support
	\item Privacy
	\item GATT server API
	\item Register Application API
	\item Better connection management
	\item Characteristic descriptors
\end{itemize}
More such issues can be found in the TODO file of Bluez source code package.
